PWNCAT2

### 2012-06-08 pwncatalog/PWNCAT2/paper/subsections/offpeak_results.tex
rename

First, we tested the sources to see if they
were spatially extended. The localization results are in \tabref{offpeak}.

@@

@@

We tested all sources for variability.

Special cases:
\begin{itemize}
  \item Crab has a funny spectrum, we have (so far) fixed it to
  \item \velax
\end{itemize}

>>>>

Following the procedure described in \subsecref{off_peak_analysis},
we performed an analysis of the off-peak emission for all 107
pulsars in this catalog. In this paper, we will present
a condensed summary of the results. We will also
describe a supplemental \fits-format table which will contain
the full spectral and spatial results for each region.

Table 
First, we tested the sources to see if they
were spatially extended. The localization results are in \tabref{offpeak}.

@@

\todo[inline]{Finally, a description of the acompanying fits table}

@@

\todo[inline]{We tested all sources for variability.}

\todo[inline]{Describe upper limits}

Special cases:
\begin{itemize}
  \item Crab has a funny spectrum, we have (so far) fixed it to
  \item \velax Spatialmodel
\end{itemize}

Results:
\begin{itemize}
  \item List of all XXX detections detected
  \item For each pulsar, is it a 
    \begin{itemize}
      \item Magnetospheric emission
      \item PWN emission
      \item Region where the fit shows trouble for some reason.
    \end{itemize}
\end{itemize}
